Supplementary material

### 2020-04-30 analysis/paper/supplementary.Rmd
- Co-author changes
- Added material images to SI - Added material images to "analysis/figures"

@@

>>>>

```{r lpplan, fig.cap="Lapa do Picareiro excavation plan with identification of exposed deposits.", out.width = '70%', fig.align='center', echo=FALSE, fig.pos="H"}

knitr::include_graphics(here::here("analysis/figures/lp-plan.jpg"))

@@

```{r quartzbladelet, fig.cap="Lapa do Picareiro - U/Lower T - Fine quartz and rock crystal blanks and blank fragments.", out.width = '60%', fig.align='center', echo=FALSE, fig.pos="H"}

knitr::include_graphics(here::here("analysis/figures/prancha_bladelets.jpg"))

```{r corelower, echo = FALSE, fig.cap = "Vale Boi - Lower 5. Chert and iron oxide (upper right) cores with vectorized scar negatives and scar directionality.", fig.align= 'center', out.width = '80%', fig.pos="H"}

knitr::include_graphics(here::here("analysis/figures/coreL.jpg"))

```{r coreupper, echo = FALSE, fig.cap = "Vale Boi - Upper 5/4E. Chert cores with vectorized scar negatives and scar directionality.", fig.align= 'center', out.width = '80%', fig.pos="H"}

knitr::include_graphics(here::here("analysis/figures/coreU.jpg"))

```{r vct, fig.cap="Vale Boi - Vale Comprido points in dolerite, chert and chalcedony.", out.width = '70%', fig.align='center', echo=FALSE}

knitr::include_graphics(here::here("analysis/figures/prancha_vct.jpg"))

```{r vct2, fig.cap="Vale Boi - Vale Comprido points in dolerite.", out.width = '60%', fig.align='center', echo=FALSE}

knitr::include_graphics(here::here("analysis/figures/prancha_vct2.jpg"))

```{r lpblades, fig.cap="Lapa do Picareiro - Middle T - Chert blades with similarities to Vale Comprido technology.", out.width = '60%', fig.align='center', echo=FALSE}

knitr::include_graphics(here::here("analysis/figures/prancha_blades.jpg"))
